\documentclass{article}
\title{Team Contract}
\author{Jess Kenney (jessk)\\Miles Steele (mlsteele)\\Anna Walsh (awalsh28)}
\begin{document}
\maketitle
\section{Goals}
\begin{itemize}
\item Make a sweet pingball that is SFB, RFC, ETU!
\item We all want to practice having a functional team that works together with minimal toe-stepping and has fun.
\end{itemize}

\section{Meetings}
\begin{itemize}
\item We will meet in our dorm.
\item \textbf{We will use class time to work on the project or explicitly spend that amount of time working later in the next few days if we miss the time.}
\item We will meet at least 3 times a week outside of class.
\item Jess will take minutes of our meetings and distribute them via email.
\end{itemize}

\section{Work}
\begin{itemize}
\item The project will take ~10 hours per person / I have no idea / We will see after our first meeting when reviewing the spec together.
\item In our meetings we will determine milestones with deadlines for specs, tests, implementation, and debugging.
\item We will distribute work evenly by carving the problem into discrete modules. We will spend some time together creating specs for the interfaces and then each dive in to implement. We will use the nose game to resolve serious disputes.
\item \textbf{We will record the assignment of responsibilities in the file \texttt{WHODIDWHAT.md} in our repo.}
\item If someone misses a deadline or cannot fulfill a commitment they will be forgiven immediately and we will find another way.
\item Every commit will be code reviewed by at least one other member of the team. We will code review using github's commenting feature. We will make a private repo to do this. We will commit both to github and to athena. If this strategy turns out to be crazy, we'll find a less complicated solution to code reviewing, but the code will be reviewed!
\item Some people like to work up against a deadline. Those people will be given earlier deadlines.
\end{itemize}

\section{Decision Making}
\begin{itemize}
\item If there is a design decision dispute then we will enumerate a list of pros and cons and make a decision as a team.
\end{itemize}

\section{Misc}
\begin{itemize}
\item All of our email communication between team members will be gpg encrypted.
\item If the gpg encryption thing turns out to infeasible, we will resort to physical letters that combust after reading.
\item If the letters are also not a plan, we can just talk to each other and accept the security risk.
\item We will give our TA access to our github repo so that she can stay in the know about our process including code that has not yet been reviewed and is thus not on athena.
\end{itemize}

\section{Look, we have our first deadline}
\begin{itemize}
\item Each member will complete their own warmup by Wednesday at 10pm which will be code reviewed that night.
\end{itemize}
\end{document}